---
title: "Welcome"
author: "Dionne Argyropoulos"
date: 2025-07-29
---

This collection was inspired by [Chrissy Roberts' Code Book](https://chrissyhroberts.github.io/Code_Book/), which I was introduced to by [Caitlin Bourke](https://github.com/BourkeCaitlin). It brings together the most useful pieces of code I’ve accumulated over the years—scripts I often return to or have developed for specific analyses. My hope is that future me (and anyone else who happens to come across this) finds it a helpful and practical resource.

Here are a list of my favourite R packages that will be leveraged throughout this section.

## Data Wrangling

```{r}
library(tidyverse)
library(janitor)
```

## Epidemiology / Statistical Analysis

```{r}
library(tidyverse)
library(janitor)
library(gtsummary)
```

## Population Genetics Analysis

```{r}
library(poppr)
library(adegenet)
```

## R Shiny

```{r}
library(shiny)
library(shiny.fluent)
library(waiter)
```

## R Package Development

```{r}
library(devtools)
library(usethis)
```

## General Git things

### Making changes {#git-changes}

```{html}
git add .
git commit -m "Add a personalised and detailed message"
git push
```

### Clone a repository from GitHub

```{html}
git clone <<INSERT GITHUB REPOSITORY>>
```

### How to remove a repository on Github

1.  Go to the repository’s main page on GitHub (e.g., https://github.com/yourusername/pvsero)
2.  Click Settings (right-hand tab)
3.  Scroll all the way to the Danger Zone at the bottom
4.  Click Delete this repository
5.  GitHub will ask you to:
    -   Confirm the name of the repo (e.g., yourusername/pvsero)
    -   Type it in to confirm
6.  Click the red I understand the consequences, delete this repository button

The repository will be permanently deleted — this action cannot be undone.

This does not delete your local R project or files — only the copy on GitHub. If you want to disconnect GitHub but keep the local Git repo, you can just remove the remote link using: git remote remove origin
