---
title: "Webscraping"
---

:::{.callout-info}
## What is Webscraping?

Webscraping is a tool to extract data from web pages. The term usually refers to an automated process which is faster and less error-prone than gathering data by hand. 

**Each web page includes**: 

- **HTML** (HyperText Markup Language: web page infrastructure), 
- **CSS** (appearance of a site), and 
- **JavaScript** (behaviour of a page)

A comprehensive tutorial has been written in the [R for Data Science (2e) Book](https://r4ds.hadley.nz/webscraping.html). Another useful tutorial that I used to guide my analysis is from the [Stats and R Blog](https://statsandr.com/blog/web-scraping-in-r/).

:::

```{r}
library(tidyverse)
library(rvest) # helps to scrape information from web pages
library(xml2) # wrapper around libxml2 C library that makes it easier to work with XML and HTML in R 
```

## Extracting Habitats

To get started scraping, you will need the URL of the page you want to scrape. Here, I had to use `read_html_live()` rather than `read_html()`. This is because [`read_html()`](https://rvest.tidyverse.org/reference/read_html.html) downloads raw static HTML from the server whereas [`read_html_live()`](https://rvest.tidyverse.org/reference/read_html_live.html) loads the page in a real brower with JavaScript and in my case, the tables only exist AFTER JavaScript runs. 

```{r}
habitat_pg  <- read_html_live("https://games.gg/pokemon-pokopia/guides/pokemon-pokopia-how-to-build-every-habitat/")

tables <- habitat_pg %>% 
  html_elements("table")

tables_parsed <- tables %>% 
  map(html_table)

habitats <- tables_parsed %>%
  map(~ mutate(.x, across(everything(), as.character))) %>%
  bind_rows()
```

## Extracting Recipes 

```{r}
base_url <- "https://www.serebii.net/pokemonpokopia/crafting.shtml"

recipe_pg <- read_html(base_url)

# Extract Titles
titles <- recipe_pg %>%
  html_elements("h2, h3") %>%
  html_text2()

# Extract Tables
tables <- recipe_pg %>%
  html_elements("table.dextable") %>%
  html_table(fill = TRUE)

tidy_tables <- map(tables, ~ .x %>%
  # Use first row as column names  
  setNames(.[1, ]) %>%
  
  # Clean column names  
  janitor::clean_names() %>%
  
  # Merge requirements columns  
  unite("requirements", requirements:last_col(), sep = ", ", na.rm = TRUE) %>%
  
  # Remove unwanted rows  
  filter(!str_detect(name, "\\*")) %>%
  
  # Remove picture column  
  select(-picture) %>%
  
  # Remove first row  
  slice(-1) %>%
  
  # Standard fix
  mutate(locations = ifelse(
    locations == "Daily Shop SpecialSparkling Water",
    "Daily Shop Special, Sparkling Water",
    locations
  ))
)

tidy_tables <- map2(
  tidy_tables,
  titles,
  ~ mutate(.x, type = .y)
)

recipes <- bind_rows(tidy_tables)
```

## Automatic scraping 

<!-- We can automate this: -->

<!-- ```{r} -->
<!-- scrape_pg <- function(url){ -->
<!--   tryCatch({ -->
<!--     read_html(url) %>%  -->
<!--       html_elements("table") %>% -->
<!--       html_table() %>% -->
<!--       # Bind and remove unnecessary lists -->
<!--       list_rbind() %>% -->
<!--       # Reduce redundancy -->
<!--       distinct(Image, Type, .keep_all = T) -->
<!--   }, error = function(e) NULL ) -->
<!-- } -->

<!-- recipes_all <- map_dfr(base_url, scrape_pg) -->

<!-- recipes_all -->
<!-- ``` -->

```{r}
base_url <- "https://www.ign.com/wikis/pokemon-pokopia/DIY_Recipes"

scrape_all_pages <- function(start_url) {
  
  all_data <- list()
  url <- start_url
  
  repeat {
    
    message("Scraping: ", url)
    
    page <- tryCatch(read_html(url), error = function(e) NULL)
    
    if (is.null(page)) break
    
    # Extract table
    page_data <- page %>%
      html_elements("table") %>%
      html_table() %>%
      list_rbind()
    
    if (nrow(page_data) == 0) break
    
    all_data[[length(all_data) + 1]] <- page_data
    
    # Find the "next" page link
    next_link <- page %>%
      html_element(".pagination-next a") %>%
      html_attr("href")
    
    # Stop if no next page
    if (is.na(next_link) || is.null(next_link)) break
    
    url <- paste0("https://www.ign.com", next_link)
  }
  
  bind_rows(all_data)
}

recipes_all <- scrape_all_pages(base_url) %>%
  distinct(Image, Type, .keep_all = TRUE)

recipes_all
```

